---
title: "R_Module5_Practice_Problem"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R-Class Module 5 Practice Problem 1

#### 1. Construct a function c_to_f(): Convert Celsius to Fahrenheit
* Input: Celsius
* Statement: Fahrenheit = Celsius*1.8+32
* Output: Fahrenheit
```{r}
c_to_f = function(Celsius) {
        Fahrenheit = Celsius * 1.8 + 32
        return(Fahrenheit)
}
```

#### 2. Convert 26 Celsius to Fahrenheit
```{r}
c_to_f(26)
```


## R-Class Module 5 Practice Problem 2

#### 1. Download the data file from 
https://www.dropbox.com/s/yy64i1ekeoo9wga/nyc_flights.csv?dl=0
(CSV) 
https://www.dropbox.com/s/4hj71qxh1a8r23e/nyc_flights.RData?dl=0 
(RData)

#### 2. Import nyc_flights.csv to the R environment, save as a data.frame “flights”

```{r}
flights <- read.csv("/Users/hyeonwooyang/Desktop/Desktop/0_WUSTL/0_Business_Analytics/02_pre_coursework/01_Intro_to_R_Programming/Project/My_R_Project/data/nyc_flights.csv")
```

#### 3. Write your code to answer the following question  
How many flights are observed?
```{r}
nrow(flights)
```
How many flights are observed each month?
```{r}
table(flights$month)
```
What is the maximum dep_delay(departure delay time)?
```{r}
# install.packages("dplyr")
library(dplyr)

summarise(flights, max(dep_delay, na.rm = TRUE))
```
What is the maximum air_time?
```{r}
summarise(flights, max(air_time, na.rm = TRUE))
```

#### 4. Create a new object flights_sample with the first 1000 rows of flights
```{r}
flights_sample <- flights[1:1000, ]
```

#### 5. Save the flights_sample to a RData file “flights_sample.RData”
```{r}
save(flights_sample, file = "flights_sample.RData")
```

#### 6. Remove the object flights_sample from the environment.
```{r}
rm(flights_sample)
```

#### 7. Load the object flights_sample from the RData file. 
```{r}
load("flights_sample.RData")
```


## R-Class Module 5 Practice Problem 3

#### 1. Create a new data.frame “flights_1” with the month, day, origin, dest, air_time columns from flights
```{r}
flights_1 <- select(flights, month, day, origin, dest, air_time)
```

#### 2. Order “flights_1” by ascending air_time
```{r}
flights_1 <- arrange(flights_1, air_time)
```

#### 3. Print the first 10 rows of “flights_1”
```{r}
flights_1[1:10, ]
```

#### 4. Calculate the average air_time for all the flights whose origin is LGA on January 1st
```{r}
filter(flights_1, month == 1, day == 1, origin == "LGA") %>%
        summarise(mean(air_time, na.rm = TRUE))
```

## R-Class Module 5 Practice Problem 4

#### 1. Group the flights by route: origin+dest
```{r}
flights %>%
        group_by(origin, dest)
```
#### 2. Calculate  the  total  number  of  flights,  average  dep_delay,  average arr_delay for each route
```{r}
flights %>%
        group_by(origin, dest) %>%
        summarise(flights = n(),
                  avg_dep_delay = mean(dep_delay, na.rm = TRUE),
                  avg_arr_delay = mean(arr_delay, na.rm = TRUE))
```
#### 3. Order the return by descending avearge dep_delay time
```{r}
flights %>%
        group_by(origin, dest) %>%
        summarise(flights = n(),
                  avg_dep_delay = mean(dep_delay, na.rm = TRUE),
                  avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
        arrange(desc(avg_dep_delay))
```

#### 4. Group the flights by carrier
```{r}
flights %>%
        group_by(carrier)
```
#### 5. Calculate  the  total  number  of  flights,average  dep_delay,  average arr_delay, total distance covered for each carrier
```{r}
flights %>%
        group_by(carrier) %>%
        summarise(flights = n(),
                  avg_dep_delay = mean(dep_delay, na.rm = TRUE),
                  avg_arr_delay = mean(arr_delay, na.rm = TRUE),
                  total_distance = sum(distance)
                  )
```
#### 6. Order the return with descending avg_arr_delay
```{r}
flights %>%
        group_by(carrier) %>%
        summarise(flights = n(),
                  avg_dep_delay = mean(dep_delay, na.rm = TRUE),
                  avg_arr_delay = mean(arr_delay, na.rm = TRUE),
                  total_distance = sum(distance)
                  ) %>%
        arrange(desc(avg_arr_delay))
```



## R-Class Module 5 Practice Problem 5

#### Plot barplot with ggplot
#### 1. A bar plot on count of flights for each weekday
```{r}
# install.packages("lubridate")
library(lubridate)
# install.packages("ggplot2")
library(ggplot2)

flights$weekday = weekdays(ymd_hms(flights$time_hour))

ggplot(flights) + geom_bar(aes(x = weekday))
```
#### 2. A  colored  bar  plot  on  count  of  flights  for  each  weekday  from  each origin
```{r}
ggplot(flights) + geom_bar(aes(x = weekday, fill = origin))
```
#### 3. Add a titile “Weekday Flights From Each NYC Airport” to your plot 
```{r}
ggplot(flights) + geom_bar(aes(x = weekday, fill = origin)) + labs(title = "Weekday Flights From Each NYC Airport")
```

#### Plot scatter point plot with ggplot
#### 4. A scatter plot on distance for each airport

#### 5. X axis is origin

#### 6. Y axis is distance
```{r}
ggplot(flights) + geom_point(aes(x = origin, y = distance))
```
