---
title: "R_Module6_Practice_Problem"
output: html_document
date: '2022-08-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R-Class Module 6 Practice Problem 1

#### Refer  to  the  daily  sales-advertising  data  of  a  chocolate  store  presented  in the table.

#### Conduct a hypothesis test (at α = 0.05) to determine if sales (y) is linearly related to advertising expenditure.

```{r}
Sales <- c(1097, 1187, 1152, 1112, 1131, 1157, 1128, 1197, 1170, 1139)
Advertisement <- c(50, 100, 75, 50, 60, 70, 75, 100, 80, 75)

df1 <- cbind(Sales, Advertisement)
df1 <- as.data.frame(df1)
df1

LinReg.Model <- lm(Sales ~ Advertisement, data = df1)
summary(LinReg.Model)
```

There is a statistically significant evidence at 0.05 significance level that Sales and Advertisement have a positive, linear relationship.


## R-Class Module 6 Practice Problem 2
#### A construction company employs three sales engineers. Engineers 1, 2, and 3 estimate the costs of 30%, 20%, and 50%, respectively, of all jobs bid by the company. For i = 1, 2, 3 define Ei to be the event that a job is estimated by engineer i. The following probabilities describe the rates at which the engineers make serious errors in estimating costs:P(error/E1) = 0.01, P(error/E2) = 0.03, and P(error/E3) = 0.02  
#### Given there was an error, what is the probability that Engineer 3 made the error?estimated by engineer i. The following probabilities describe the rates at which the engineers make serious errors in estimating costs: P(error/E1) = 0.01, P(error/E2) = 0.03, and P(error/E3) = 0.02  

#### Given there was an error, what is the probability that Engineer 3 made the error?

```{r}
library(LaplacesDemon)

Prior = c(0.3,0.2,0.5)
Likelihood = c(0.01, 0.03, 0.02)

BayesTheorem(Prior,Likelihood)
```
The probability that Engineer 3 made the error is 0.5263.

