---
title: "R_Module2_Practice_Problem"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R-Class Module 2 Practice Problem 1

#### 1. Create an empty numeric vector nv1 of length 6
```{r}
nv1 <- numeric(6)
nv1
```
#### 2. Create a numeric vector nv2 with even numbers from 2 to 20(2,4,. . . 20)
```{r}
nv2 <- seq(from = 2,to = 20, by = 2)
nv2
```
#### 3. How many elements are there in nv2?
```{r}
length(nv2)
```
#### 4. What is the 6th element of nv2?
```{r}
nv2[6]
```
#### 5. Add a new value 22 to the end of nv2
```{r}
nv2 <- c(nv2, 22)
nv2
```
#### 6. Delete 2 from nv2
```{r}
nv2 <- nv2[-1]
```
#### 7. Print your new nv2
```{r}
nv2
```
#### 8. Caluclate the mean(),min(),max(),sd() of nv2
```{r}
mean(nv2)
min(nv2)
max(nv2)
sd(nv2)
```
#### 9. Create a numeric vector nv3 from 1 to 10
```{r}
nv3 <- 1:10
nv3
```
#### 10. Add 3 to each element of nv3
```{r}
nv3 <- nv3 + 3
nv3
```
#### 11. Coerce nv3 to character
```{r}
nv3 <- as.character(nv3)
```
#### 12. Print the new nv3 
```{r}
nv3
```

## R-Class Module 2 Practice Problem 2  

#### 1. Use seq() to generate a vector v3 of length 15, odd numbers from 1 to 
29
```{r}
v3 <- seq(from = 1, to = 29, by = 2)
v3
```
#### 2. Use matrix() to construct m1 of 3*5 from v3, fill by column
```{r}
m1 <- matrix(data = v3, nrow = 3, ncol = 5)
m1
```
#### 3. Use matrix() to construct m2 of 5*3 from v3, fill by column
```{r}
m2 <- matrix(data = v3, nrow = 5, ncol = 3)
m2
```
#### 4. Add 1 to each element of m1
```{r}
m1 + 1
```

