---
title: "R_Module4_Practice_Problem"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R-Class Module 4 Practice Problem 1

#### 1. Create a data.frame called running with the following data
```{r}
running <- data.frame(Name = c("Sally", "Mike", "Carol"), Gender = c("F", "M", "F"), TenK = c(55, 46, 62), PR = c(52, 44, 58), Qualified = c(FALSE, TRUE, FALSE))
running
```

#### 2. Add the following column to running
```{r}
running$HalfMarathon = c(120, 100, 140)
running
```

#### 3. Add the following row to running
```{r}
newRow = data.frame(Name = "Sage", Gender = "M", TenK = 40, PR = 42, Qualified = TRUE, HalfMarathon = 81)
running <- rbind(running, newRow)
running
```

## R-Class Module 4 Practice Problem 2

#### 1. Create a list new_list with the following members

- 1st member: a vector of length 10 from uniform distribution from -2 to 2  
- 2nd member: a matrix from 1:10, with 2 rows, 5 columns, fill by row
- 3rd member: the running data.frame
```{r}
new_list <- list(runif(10, -2, 2), matrix(1:10, 2, 5, byrow = TRUE), running)
new_list
```

#### 2. Add 2 to each element of the first member of new_list
```{r}
new_list[[1]] + 2
```

#### 3. Calculate the sum of the 2nd member of new_list
```{r}
sum(new_list[[2]])
```

#### 4. Remove the 3rd member of new_list
```{r}
new_list[[3]] = NULL
new_list
```


## R-Class Module 4 Practice Problem 3

#### 1. Create  a  ordered  factor  mons  from  the  following  character  vector: 
c(“March”,“April”,“January”,“November”,“January”,“September”,“Octo
ber”,“September”,“November”,“August”,“January”,“November”,“Nove
mber”,“February”,“May”,““July”,“December”,“August”,“August”,“Septe
mber”,“November”, “February”,“April”)
```{r}
mons <- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","July","December","August","August","September","November","February","April")
factor(mons, levels = c("January", "February", "March","April", "May", "June", "July", "August", "September", "October", "November","December"), ordered = TRUE)
```

#### 2. Count the occurrence of each month
```{r}
table(mons)
```

#### 3. Create a factor factor_weight with the weight of women of 2 levels
```{r}
head(women)
factor_weight <- cut(women$weight, 2, labels = c("Low", "High"))
```

#### 4. Assign levels of “Low” and “High” to the factor 
```{r}
table(factor_weight)
```
